Statistical Theory\\ Chess Dataset Analysis

### 2024-09-30 Article/Article.tex
Updated src

\subsection{Nelder - Mead optimization method}

>>>>

\subsection{Nelder - Mead optimization method}
The Nelder-Mead optimization method is a direct search algorithm used for solving unconstrained nonlinear optimization problems without requiring gradient information. It operates on a simplex, a geometric shape consisting of $n+1$ vertices in an $n$-dimensional space. The algorithm iteratively updates this simplex by reflecting, expanding, contracting, or shrinking its vertices to explore the search space. These transformations aim to minimize an objective function $f(x)$ through comparisons of function values at the simplex vertices. Despite its simplicity, the method is known for efficiency in practice but does not guarantee convergence to a global minimum, especially in higher-dimensional or highly non-convex landscapes. It is widely applied in scenarios where gradient information is unavailable or expensive to compute.
